Preventing runtime errors of Redis at compile time

### 2015-11-19 paper.tex
8. Discussions: Redis Transactions

\footnotetext{Hedis provides another kind of context, \mintinline{haskell}{RedisTx}, for \emph{transactions}, united with \mintinline{haskell}{Redis} under the class of \mintinline{haskell}{RedisCtx}. We demonstrate \mintinline{haskell}{Redis} only for brevity. }

@@

>>>>

\footnotetext{Hedis provides another kind of context, \mintinline{haskell}{RedisTx}, for \emph{transactions}, united with \mintinline{haskell}{Redis} under the class of \mintinline{haskell}{RedisCtx}. We are demonstrating \mintinline{haskell}{Redis} only for brevity. }

@@

Redis provides transactions, another context for executing commands.
Redis trasanctions are atomic in the sense that, all commands in a transaction
 will executed sequentially, and no other requests issued by other clients will
 be served in the middle.\footnotemark In contrast, we cannot make such
 guarantee in the ordinary context, which may destroy the assertions we made
 in types.

At the point of writing, transactions are not supported in our implementation.
 We are planning to add it in the future, and we are expecting that there
 wouldn't be much difficulties, since we've implemented a runtime type checker
 specifically targeting Redis transactions once, before we moved on to the
 types.

\footnotetext{\url{http://redis.io/topics/transactions}}
